\documentclass[openany]{book}

\usepackage{hyperref}
\usepackage[
  type={CC},
  modifier={by-sa},
  version={4.0},
]{doclicense}


%% Macro definitions
\newcommand{\warning}[1]{\textbf{\textit{WARNING: #1}}}
\newcommand{\GNUBaseballCap}{\href{https://shop.fsf.org/caps/gnu-baseball-cap}{GNU Baseball Cap}}
\newcommand{\EmacsMug}{\href{https://shop.fsf.org/gear/emacs-auto-fill-mode-mug}{Emacs auto-fill-mode Mug}}
\newcommand{\Labrador}{\href{https://en.wikipedia.org/wiki/Labrador\_Retriever}{Labrador}}
\newcommand{\GreyParrot}{\href{https://en.wikipedia.org/wiki/Grey\_parrot}{Grey parrot}}
\newcommand{\CatsName}{Cats'); DROP TABLE users; --}

\begin{document}
\title{The Lost Spoon}
\author{Ron}
\date{2019-10-24}
\maketitle

\begin{chapter}{Meta-introduction}
  \doclicenseThis
  \warning{This book is fake/fiction}
  \newline
  This book is written in the past-tense
\end{chapter}

\begin{chapter}{Introduction}
  There was a person called Bob.
  Bob had a luxury spoon that he kept on a stand in the spoonery\footnote{A place where spoons are kept, spoon-room}.
\end{chapter}

\begin{chapter}{Spoon is lost}
  Bob woke up, he went to the spoonery and the spoon was not where he had put it.
  He found muddy footprints, and a \GNUBaseballCap, which had been forgotten by the stealer.
  He reported this to the police.
\end{chapter}

\begin{chapter}{Stealer has camomile tea}
  The next day Bob woke up, and found that one of his camomile teabags was missing, the \GNUBaseballCap{} was missing,
  and he found an \EmacsMug{} on his table, the stealer had came back to collect his \GNUBaseballCap, and drink some camomile tea,
  and had forgotten his \EmacsMug.
\end{chapter}

\begin{chapter}{The stealer's dog}
  The next day Bob woke up, and found that the \EmacsMug{} was missing, his luxury fork was missing,
  and now there was a \Labrador{} in his house.
  The \Labrador's collar did not have any information on it except ``This is \CatsName's dog, \CatsName{} likes free software, and camomile tea''.
  The stealer had came back to collect his \EmacsMug, steal Bob's luxury fork, and had left his \Labrador.
\end{chapter}

\begin{chapter}{The stealer takes his dog back, and Bob gets better security}
  \section{The stealer take his dog back}{
    The next day when Bob woke up, he found that the \Labrador{} was missing, this time the stealer had not forgotten anything.
  }
  \section{Bob gets better security}{
    Bob also improved his security, so that the Stealer could not get back in again.
  }
\end{chapter}

\begin{chapter}{The stealer has some camomile tea, and leaves a \GreyParrot{} at Bob's neighbour's house}
  Since Bob has improved his security, the stealer decided to go to Bob's neighbour's house.
  The stealer had some camomile tea at Bob's neighbour's house, and had also left his \GreyParrot.
  The \GreyParrot{} said the stealer's full name\footnote{``Cats'); DROP TABLE users; --'' was the stealer's name} and address,
  and \CatsName{} was found to have all of the stolen items,
  the \GNUBaseballCap, the \EmacsMug, the \Labrador, and the \GreyParrot.
  Cats'); DROP TABLE users; -- returned all of the stolen items (the 2 camomile teabags\footnote{Not the same ones, he bought new ones},
  and the luxury spoon and fork).
  The \GreyParrot{} also got returned to Cats'); DROP TABLE users; --.
\end{chapter}

\end{document}
